% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{Group Contributions}

% Please do not change the subtitle
\subtitle{Group Project}

% Please put your student number in the author field
\author{1607934}

\begin{document}

\maketitle

\abstract{I will be listing my group contributions here. While the project was twelve weeks, the last two were content locked and used for polishing.}

\newpage
\clearpage

\section*{}


\subsection*{Sprint 1}

For the most part of our first sprint, I used my time to learn how to use Unreal Engine by looking at tutorials and trying my hand in simple blueprint exercises. 

\subsection*{Sprint 2}

The second week consisted of more UE4 practise and general ideation of our game and what features it would need.

\subsection*{Sprint 3}

This week I managed to create a very rough inventory prototype with received help online. I should be able to polish it, although will need to know a bit more from the team about how we want it to work in-game as it differs from traditional inventory systems.

\subsection*{Sprint 4}

This week I sent an email to the technician, Andy, to set up our SVN server for us. It took a while to get used to as we primarily used Github for version control, although shouldn't take as long to learn as it took for us with Github.

\subsection*{Sprint 5}

This week I set aside the inventory system temporarily as we still lacked assets to work with it anyways. I started working on an environmental asset, a lava blueprint, which should be placeable on static meshes. This was done successfully. 

\subsection*{Sprint 6}

This week I wasn't sure what to do as most tasks were taken, so I decided to try my hand in ragdolling upon death for the enemies. It took a few tries due to the overlapping issues that would occur when the weapon hitbox and enemy collide, but eventually got working.

\subsection*{Sprint 7}

This week I thought of a cool idea which I managed to implement: falling destructable rocks from the skybox. I then asked a BSc group member, Max, to help me figure out how to make the rocks instakill anyone they fall on. We eventually got that working as well.

\subsection*{Sprint 8}

This week I added another environmental asset: rocks with glowing cracks. It blended in nicely with the lava. Because why not?

\subsection*{Sprint 9}

This week I spent the majority of my time learning the built-in `sequencer' feature for our trailer. Eventually, I got some good cinematic footage.  

\subsection*{Sprint 10}

During the final week I spent, again, the majority of my time on our trailer and polishing it. While I wish I had more time to spend on it, I think the final result came out satisfactory. 


\end{document}